Gammapy: A Python package for gamma-ray astronomy

### 2023-08-25 src/ms-review.tex
Update ms-review.tex

\author{
        Axel Donath \thanks{Mail inquiries to:
        \href{mailto:GAMMAPY-COORDINATION-L@IN2P3.FR}{GAMMAPY-COORDINATION-L@IN2P3.FR}} \inst{\ref{inst:001}} \and
        Régis Terrier \inst{\ref{inst:002}} \and
        Quentin Remy \inst{\ref{inst:003}} \and
        Atreyee Sinha \inst{\ref{inst:004}} \and
        Cosimo Nigro \inst{\ref{inst:005}} \and
        Fabio Pintore \inst{\ref{inst:006}} \and
        Bruno Khélifi \inst{\ref{inst:002}} \and
        Laura Olivera-Nieto \inst{\ref{inst:003}}\and
        Jose Enrique {Ruiz} \inst{\ref{inst:007}} \and
        Kai Brügge \inst{\ref{inst:008},\ref{inst:009}} \and
        Maximilian Linhoff \inst{\ref{inst:009}} \and
        Jose Louis {Contreras} \inst{\ref{inst:004}} \and
        Fabio Acero \inst{\ref{inst:010}} \and
        Arnau Aguasca-Cabot \inst{\ref{inst:011}, \ref{inst:012}, \ref{inst:013}, \ref{inst:014}} \and
        David Berge \inst{\ref{inst:015}, \ref{inst:016}} \and
        Pooja Bhattacharjee \inst{\ref{inst:017}} \and
        Johannes Buchner \inst{\ref{inst:018}} \and
        Catherine Boisson \inst{\ref{inst:019}} \and
        David {Carreto Fidalgo} \inst{\ref{inst:020}} \and
        Andrew Chen \inst{\ref{inst:021}} \and
        Mathieu {de Bony de Lavergne} \inst{\ref{inst:017}} \and
        José Vinícius {de Miranda Cardoso}\inst{\ref{inst:022}} \and
        Christoph Deil \inst{\ref{inst:003}} \and
        Matthias Fü{\ss}ling \inst{\ref{inst:023}} \and
        Stefan Funk \inst{\ref{inst:024}} \and
        Luca Giunti \inst{\ref{inst:002}} \and
        Jim Hinton \inst{\ref{inst:003}} \and
        Léa Jouvin \inst{\ref{inst:025}} \and
        Johannes King \inst{\ref{inst:026}, \ref{inst:003}} \and
        Julien Lefaucheur \inst{\ref{inst:027}, \ref{inst:002}} \and
        Marianne Lemoine-Goumard \inst{\ref{inst:028}} \and
        Jean-Philippe Lenain \inst{\ref{inst:029}} \and
        Rub{\'e}n L{\'o}pez-Coto \inst{\ref{inst:007}} \and
        Lars Mohrmann \inst{\ref{inst:003}} \and
        Daniel Morcuende \inst{\ref{inst:004}} \and
        Sebastian Panny \inst{\ref{inst:032}} \and
        Maxime Regeard \inst{\ref{inst:002}} \and
        Lab Saha \inst{\ref{inst:004}} \and
        Hubert Siejkowski \inst{\ref{inst:030}} \and
        Aneta Siemiginowska \inst{\ref{inst:001}} \and
        Brigitta M. {Sipőcz} \inst{\ref{inst:031}} \and
        Tim Unbehaun \inst{\ref{inst:024}} \and
        Christopher {van Eldik} \inst{\ref{inst:024}} \and
        Thomas Vuillaume \inst{\ref{inst:017}} \and
        Roberta Zanin \inst{\ref{inst:023}}
}

>>>>

\author{
        Axel Donath \thanks{Mail inquiries to:
        \href{mailto:GAMMAPY-COORDINATION-L@IN2P3.FR}{GAMMAPY-COORDINATION-L@IN2P3.FR}} \inst{\ref{inst:001}} \and
        Régis Terrier \inst{\ref{inst:002}} \and
        Quentin Remy \inst{\ref{inst:003}} \and
        Atreyee Sinha \inst{\ref{inst:004}} \and
        Cosimo Nigro \inst{\ref{inst:005}} \and
        Fabio Pintore \inst{\ref{inst:006}} \and
        Bruno Khélifi \inst{\ref{inst:002}} \and
        Laura Olivera-Nieto \inst{\ref{inst:003}}\and
        Jose Enrique {Ruiz} \inst{\ref{inst:007}} \and
        Kai Brügge \inst{\ref{inst:008},\ref{inst:009}} \and
        Maximilian Linhoff \inst{\ref{inst:009}} \and
        Jose Luis {Contreras} \inst{\ref{inst:004}} \and
        Fabio Acero \inst{\ref{inst:010}} \and
        Arnau Aguasca-Cabot \inst{\ref{inst:011}, \ref{inst:012}, \ref{inst:013}, \ref{inst:014}} \and
        David Berge \inst{\ref{inst:015}, \ref{inst:016}} \and
        Pooja Bhattacharjee \inst{\ref{inst:017}} \and
        Johannes Buchner \inst{\ref{inst:018}} \and
        Catherine Boisson \inst{\ref{inst:019}} \and
        David {Carreto Fidalgo} \inst{\ref{inst:020}} \and
        Andrew Chen \inst{\ref{inst:021}} \and
        Mathieu {de Bony de Lavergne} \inst{\ref{inst:017}} \and
        José Vinícius {de Miranda Cardoso}\inst{\ref{inst:022}} \and
        Christoph Deil \inst{\ref{inst:003}} \and
        Matthias Fü{\ss}ling \inst{\ref{inst:023}} \and
        Stefan Funk \inst{\ref{inst:024}} \and
        Luca Giunti \inst{\ref{inst:002}} \and
        Jim Hinton \inst{\ref{inst:003}} \and
        Léa Jouvin \inst{\ref{inst:025}} \and
        Johannes King \inst{\ref{inst:026}, \ref{inst:003}} \and
        Julien Lefaucheur \inst{\ref{inst:027}, \ref{inst:002}} \and
        Marianne Lemoine-Goumard \inst{\ref{inst:028}} \and
        Jean-Philippe Lenain \inst{\ref{inst:029}} \and
        Rub{\'e}n L{\'o}pez-Coto \inst{\ref{inst:007}} \and
        Lars Mohrmann \inst{\ref{inst:003}} \and
        Daniel Morcuende \inst{\ref{inst:004}} \and
        Sebastian Panny \inst{\ref{inst:032}} \and
        Maxime Regeard \inst{\ref{inst:002}} \and
        Lab Saha \inst{\ref{inst:004}} \and
        Hubert Siejkowski \inst{\ref{inst:030}} \and
        Aneta Siemiginowska \inst{\ref{inst:001}} \and
        Brigitta M. {Sipőcz} \inst{\ref{inst:031}} \and
        Tim Unbehaun \inst{\ref{inst:024}} \and
        Christopher {van Eldik} \inst{\ref{inst:024}} \and
        Thomas Vuillaume \inst{\ref{inst:017}} \and
        Roberta Zanin \inst{\ref{inst:023}}
}
